---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Queue system simulator

<!-- badges: start -->
[![R-CMD-check](https://github.com/MQ-STAT1378/assignment2-question2-nzh-zhou/workflows/R-CMD-check/badge.svg)](https://github.com/MQ-STAT1378/assignment2-question2-nzh-zhou/actions)
<!-- badges: end -->

This package simulates the customer queue system of a bank. In the function `Multiserver`, input information on the customer arrival and service time and the bank's number of customer service servers.

## Installation

You can install this package via github. First, clone the repository, which can be done by running `git clone https://github.com/MQ-STAT1378/assignment2-question2-nzh-zhou` in your shell (if you have access to this repo), then running the following code in R. Don't forget to delete the cloned local repository.

``` {r github-install, eval = FALSE}
# install.packages("devtools")
devtools::install_git("https://github.com/MQ-STAT1378/assignment2-question2-nzh-zhou")
```

## Example

The data.frame `bank` simulates the customer arrival and service times of a bank. We use it here to simulate the queue system of a bank.

```{r example}
library(banksim)
head(Multiserver(bank$arrival_time, bank$service_time, 3))
```

